\section{Regular files}

\begin{crules}
    \cmust{Name file by regex} \verb/^[a-z0-9-]{1,16}\.[a-z0-9]{1,4}$/
    \cmust{Use \mbox{UTF-8} encoding to file}
    \cmust{Limit line width less than 80 characters}
    \cmust{Indent by TAB character}
\end{crules}

File's name accept more than 16 characters, why limit it less than that?.
Because file's name represent for file's content and 16 charaters are
reasonable to do that. It's long enough to explain file's content and
isn't too long to read. File extension is limit less than 4 characters for
same principle. 4 characers is enough to explain file's type and isn't
too long. If in the same directory, file's names are conflict, let move
it into other directories.

File's name also accept other characters than a-z, 0-9 and hyphen,
why limit it than that?. Because it is enough to explain file's content.
First, a-z lowercase characters uses to show main file's content.
Second, doesn't use uppercase help file's name more clearly. It also help
programmers write file's name under \mbox{command-line} interface more easy.
Third, 0-9 characters uses to specify version, date and other things.
Fourth, hyphen use to split components. No need more characters,
it only make hard to read.

\pkgname{} use ASCII characters because it only accept English, why use
\mbox{UTF-8} encoding for files?. Because \mbox{UTF-8} is default enable by
almost text editors. When programmers working with both ".h", ".c" and
\mbox{UTF-8} resources files, they no need switch editor encoding between
\mbox{UTF-8} and ASCII.

Number of characters on line doesn't limit by any file system, why limit it
less than 80 characters?. In simple, for readability. 80 characters are
comfort to read, fit with small screen and avoid too depth nested of
code blocks. Note that, 80 characters includes new line character,
so maximum number of characters on text editor is 79.

Why is TAB?. TAB or SPACE is infinite war between programmers so don't
make war here. \pkgname{} choose TAB because it require one key pressed to
indent. No talk, no war, just pick it up!.
